### 2019-04-30 draft_charts.Rmd
Update before sending for review in mid-April.

---
output:
  html_document:
    number_sections: FALSE
    self_contained: TRUE
    code_folding: hide
    toc: TRUE
    toc_float: TRUE
    css: www/web_report.css
    editor_options:
      chunk_output_type: console
editor_options:
  chunk_output_type: console
---

@@

```{r rmarkdown-setup, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

@@

* Numerator: age 70, price-adjusted, per-capita annuitized income with imputed rent and other income
* Denominator: mean price-adjusted, per-capita earnings from ages 50 to 59

@@

```{r chart1}
cohorts <- c("1936-1945", "1946-1955", "1956-1965", "1966-1975", "1976-1985")

read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%")) %>%
  filter(doby %in% cohorts) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(title = "Age 70 Percentage of People Who Fail to Replace 75% of Age 50-59 Earnings",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()   
```

@@

```{r chart1b}
cohorts <- c("1936-1945", "1946-1955", "1956-1965", "1966-1975", "1976-1985")

read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%")) %>%
  filter(doby %in% cohorts) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(title = "Age 70 Percentage of People Who Fail to Replace 80% of Age 50-59 Earnings",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()   
```

@@

```{r chart1c}
cohorts <- c("1936-1945", "1946-1955", "1956-1965", "1966-1975", "1976-1985")

read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%", "80-85%")) %>%
  filter(doby %in% cohorts) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(title = "Age 70 Percentage of People Who Fail to Replace 85% of Age 50-59 Earnings",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()   
```

@@

```{r chart1d}
cohorts <- c("1936-1945", "1946-1955", "1956-1965", "1966-1975", "1976-1985")

read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%", "80-85%", "85-90%")) %>%
  filter(doby %in% cohorts) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(title = "Age 70 Percentage of People Who Fail to Replace 90% of Age 50-59 Earnings",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()   
```

## Chart 2: Retirement Income at Age 70 is Rising

```{r chart2}
read_csv("data/figure2.csv") %>%
  filter(doby %in% cohorts) %>%
  ggplot(aes(doby, ncharts_aftertax_income_P50)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::dollar(ncharts_aftertax_income_P50, largest_with_cents = 0)), 
            vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(title = "Age-70, per-capita, price-adjusted income",
       subtitle = "Median shared annuitized income with imputed rent, other income, and taxes",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()
```

## Chart 3 (old): The Gender Gap in Retirement Income is Narrowing

```{r chart3}
read_csv("data/figure3.csv") %>%
  filter(doby %in% cohorts) %>%
  ggplot(aes(doby, ncharts_aftertax_income_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(ncharts_aftertax_income_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 0.7), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(title = "Age-70, per-capita, price-adjusted, shared annuitized income with imputed rent, other income, and taxes",
       subtitle = "By sex",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis() 
```

## Chart 3 (new): The Gender Gap in Social Secuirty Benefits is Narrowing

```{r, chart3b}
read_csv("data/figure3b.csv") %>%
  filter(doby %in% cohorts) %>%
  ggplot(aes(doby, Ownssb_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(Ownssb_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 0.7), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(title = "Median Age-70 Price-Adjusted Social Security Benefits by Sex",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis() 
```

@@

```{r chart4}
read_csv("data/figure4.csv") %>%
  filter(doby %in% cohorts) %>%
  filter(!is.na(male)) %>%
  ggplot(aes(doby, lifetime_earn_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(lifetime_earn_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 0.7), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(title = "Median Price-adjusted Earnings from Ages 25 to 69 at Age 70",
       subtitle = "By sex",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis() 
```

@@

```{r chart5}
benefits <- c("Worker only", "Worker supplemented by spousal or survivor", "Spouse or survivor only")

read_csv("data/figure5.csv") %>%
  filter(doby %in% cohorts) %>%
  select(doby,
         `Worker supplemented by spousal or survivor` = dualben_Mean,
         `Worker only` = wrkonly_Mean,
         `Spouse or survivor only` = auxonly_Mean) %>%
  gather(key = "benefit_type", value = "share", -doby) %>%
  mutate(benefit_type = factor(benefit_type, levels = benefits)) %>%
  ggplot(aes(benefit_type, share, fill = doby)) +
  geom_col(position = "dodge") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Social Security Benefit Type at Age 70 for Female Beneficiaries (%)",
       x = NULL,
       y = NULL) +
  remove_ticks()
```

## Chart 6: Racial and ethnic disparities in retirement income will narrow modestly

* We are concerned about showing this because of how racial/ethnic differences in income are estimated and projected. We don’t have a lot of certainty about how gaps will change in the future.

```{r chart6}
read_csv("data/figure6.csv") %>%
  filter(doby %in% cohorts) %>%
  filter(!is.na(raceeth)) %>%
  filter(raceeth != "4.Other") %>%
  ggplot(aes(doby, ncharts_aftertax_income_P50, fill = raceeth)) +
  geom_col(position = "dodge") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15)), 
                     labels = scales::dollar) +
  labs(title = "Age-70, per-capita, price-adjusted, shared annuitized income\nwith imputed rent, other income, and taxes",
       subtitle = "By race and ethnicity",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks()
```

## Chart 7: Social Security Remains a Key Pillar of Retirement Security {.tabset}

* Quntiles are based on per-capita, price-adjusted, shared annuitized income with imputed rent, other income, federal taxes, state taxes, payroll taxes and the Medicare surtax at age 70.
* Values are the mean of the different sources of income in each quintile.

Financial income = per-capita interest + per-capita dividends + per-capita rental income + per-capita IRA withdrawals
Other income = pcNotModel_Mean + per-capita imputed rent + per-capita other income

### All, No Imputed Rent

```{r chart7-no-imputed-rent}
incomes <- c("Other income", "Financial income", "DB pension income", "Earnings", "Social Security")

read_csv("data/figure7.csv") %>%
  filter(doby %in% cohorts) %>%
  mutate(`Financial income` = PCwlthinc_Mean + PCRetinc_Mean, 
         `Other income` = pcNotModel_Mean + pcimpr_Mean) %>%
  select(nchartQuin,
         doby,
         Earnings = PCearn_Mean, 
         `Social Security` = PCssb_Mean, 
         `DB pension income` = PCdbinc_Mean, 
         `Financial income`, `Other income`) %>%
  gather(key = "income_type", value = "income", Earnings, `Social Security`, `DB pension income`, `Financial income`, `Other income`) %>%
  mutate(income_type = factor(income_type, levels = incomes)) %>%
  ggplot(aes(as.character(nchartQuin), income, fill = income_type)) +
  geom_col(position = "fill") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     labels = scales::percent) +
  facet_wrap(~doby) +
  labs(title = "Major Sources of Income at Age 70 by Income Quintile",
       x = "Income quintile",
       y = NULL) +
  remove_ticks()  
```

### All, Imputed Rent

```{r chart7-imputed-rent}
incomes <- c("Other income", "Financial income", "DB pension income", "Earnings", "Social Security")

read_csv("data/figure7.csv") %>%
  filter(doby %in% cohorts) %>%
  mutate(`Financial income` = PCwlthinc_Mean + PCRetinc_Mean, 
         `Other income` = pcNotModel_Mean + pcimpr_Mean + pcimpr_Mean) %>%
  select(nchartQuin,
         doby,
         Earnings = PCearn_Mean, 
         `Social Security` = PCssb_Mean, 
         `DB pension income` = PCdbinc_Mean, 
         `Financial income`, `Other income`) %>%
  gather(key = "income_type", value = "income", Earnings, `Social Security`, `DB pension income`, `Financial income`, `Other income`) %>%
  mutate(income_type = factor(income_type, levels = incomes)) %>%
  ggplot(aes(as.character(nchartQuin), income, fill = income_type)) +
  geom_col(position = "fill") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     labels = scales::percent) +
  facet_wrap(~doby) +
  labs(title = "Major Sources of Income at Age 70 by Income Quintile",
       x = "Income quintile",
       y = NULL) +
  remove_ticks()  
```

### SSB > 0, No Imputed Rent

**Note:** Quintiles are based on the total age 70 population.

```{r chart7-ssb-no-imputed-rent}
incomes <- c("Other income", "Financial income", "DB pension income", "Earnings", "Social Security")

read_csv("data/figure7b.csv") %>%
  filter(doby %in% cohorts) %>%
  mutate(`Financial income` = PCwlthinc_Mean + PCRetinc_Mean, 
         `Other income` = pcNotModel_Mean + pcimpr_Mean) %>%
  select(nchartQuin,
         doby,
         Earnings = PCearn_Mean, 
         `Social Security` = PCssb_Mean, 
         `DB pension income` = PCdbinc_Mean, 
         `Financial income`, `Other income`) %>%
  gather(key = "income_type", value = "income", Earnings, `Social Security`, `DB pension income`, `Financial income`, `Other income`) %>%
  mutate(income_type = factor(income_type, levels = incomes)) %>%
  ggplot(aes(as.character(nchartQuin), income, fill = income_type)) +
  geom_col(position = "fill") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     labels = scales::percent) +
  facet_wrap(~doby) +
  labs(title = "Major Sources of Income at Age 70 by Income Quintile",
       x = "Income quintile",
       y = NULL) +
  remove_ticks()  
```

### SSB > 0, Imputed Rent

**Note:** Quintiles are based on the total age 70 population.

```{r chart7-ssb-imputed-rent}
incomes <- c("Other income", "Financial income", "DB pension income", "Earnings", "Social Security")

read_csv("data/figure7b.csv") %>%
  filter(doby %in% cohorts) %>%
  mutate(`Financial income` = PCwlthinc_Mean + PCRetinc_Mean, 
         `Other income` = pcNotModel_Mean + pcimpr_Mean + pcimpr_Mean) %>%
  select(nchartQuin,
         doby,
         Earnings = PCearn_Mean, 
         `Social Security` = PCssb_Mean, 
         `DB pension income` = PCdbinc_Mean, 
         `Financial income`, `Other income`) %>%
  gather(key = "income_type", value = "income", Earnings, `Social Security`, `DB pension income`, `Financial income`, `Other income`) %>%
  mutate(income_type = factor(income_type, levels = incomes)) %>%
  ggplot(aes(as.character(nchartQuin), income, fill = income_type)) +
  geom_col(position = "fill") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     labels = scales::percent) +
  facet_wrap(~doby) +
  labs(title = "Major Sources of Income at Age 70 by Income Quintile",
       x = "Income quintile",
       y = NULL) +
  remove_ticks()  
```

## Chart 8: Social Security’s Financing Problems Pose Additional Risks

* Among people with Social Security benefits

```{r chart8}
read_csv("data/figure8.csv") %>%
  filter(doby %in% cohorts) %>%
  select(doby,
         `Scheduled law` = PCssb_P50,
         `Payable benefits` = PCssb_payable_P50) %>%
  gather(key = "Benefit type", value = "benefit", -doby) %>%
  mutate(`Benefit type` = factor(`Benefit type`, levels = c("Scheduled law", "Payable benefits"))) %>%
  ggplot(aes(doby, benefit, fill = `Benefit type`)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(benefit, largest_with_cents = 0)), 
            vjust = -1,
             position = position_dodge(width = 0.8)) +   
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15)), 
                     labels = scales::dollar) +
  labs(title = "Median Annual Social Security Benefit at Age 70",
       subtitle = "Among People with Social Security Benefits",
       x = "Income quintile",
       y = NULL) +
  remove_ticks() +
  remove_axis()   
```

@@

With payable Social Security benefits

```{r, chart9}
read_csv("data/figure9.csv") %>%
filter(ncharts_reprate_payable %in% c("0-50%", "50-75%")) %>%
  filter(doby %in% cohorts) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(title = "Age 70 Percentage of People Who fail to Replace 75% of Age 50-59 Earnings",
       subtitle = "Social Security benefits under payable law",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()
```

>>>>

---
output:
  html_document:
    number_sections: FALSE
    self_contained: TRUE
    code_folding: hide
    toc: TRUE
    toc_float: TRUE
    css: www/web_report.css
    editor_options:
      chunk_output_type: console
self_contained: no      
editor_options:
  chunk_output_type: console
---

@@

```{r rmarkdown-setup, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

knitr::opts_chunk$set(fig.width = 6.5, fig.height = 5, fig.path = "figures/", dev = c("png", "cairo_pdf"))
```

@@

* Numerator: age 70, price-adjusted, per-capita annuitized income
* Denominator: mean price-adjusted, per-capita earnings from ages 50 to 59

```{r}
cohorts <- c("1936-1945", "1946-1955", "1956-1965", "1966-1975", "1976-1985")

#' rename_cohort
#'
#' @param x a vector with cohorts
#'
#' @return a vector of renamed cohorts
rename_cohort <- function(x) {
  cohort <- list("1936-1945" = "Pre-boomers (1936–45)", 
                 "1946-1955" = "Early boomers (1946–55)", 
                 "1956-1965" = "Late boomers (1956–65)", 
                 "1966-1975" = "Gen Xers (1966–75)", 
                 "1976-1985" = "Early Millenials (1976-1985)")

  if (is.null(cohort[[x]])) {
    print("ERROR: no cohort match")
    stop()
  } else {
    return(cohort[[x]])
  }
}

rename_cohort <- function(x, two_lines = TRUE) {
  if (two_lines == TRUE) {
    cohort <- recode(x,
      `1936-1945` = "Pre-boomers\n(1936–45)", 
      `1946-1955` = "Early boomers\n(1946–55)", 
      `1956-1965` = "Late boomers\n(1956–65)", 
      `1966-1975` = "Gen Xers\n(1966–75)", 
      `1976-1985` = "Early millenials\n(1976-1985)")

    factor(cohort, levels = c("Pre-boomers\n(1936–45)", 
                              "Early boomers\n(1946–55)", 
                              "Late boomers\n(1956–65)", 
                              "Gen Xers\n(1966–75)", 
                              "Early millenials\n(1976-1985)"))
  } else {
    cohort <- recode(x,
      `1936-1945` = "Pre-boomers (1936–45)", 
      `1946-1955` = "Early boomers (1946–55)", 
      `1956-1965` = "Late boomers (1956–65)", 
      `1966-1975` = "Gen Xers (1966–75)", 
      `1976-1985` = "Early millenials (1976-1985)")

    factor(cohort, levels = c("Pre-boomers (1936–45)", 
                              "Early boomers (1946–55)", 
                              "Late boomers (1956–65)", 
                              "Gen Xers (1966–75)", 
                              "Early millenials (1976-1985)"))
  }
}

@@

```{r chart1}
chart1 <- read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%")) %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent_format(accuracy = 0.1)(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)),
                     limits = c(0, 50)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("An Increasing Share of Retirees Won't Replace Pre-Retirement Incomes"),
      subtitler("Age 70 percentage of people who fail to replace 75% of age 50-59 earnings"),
      chart1,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2, 2, 30, 1, 1))
```

@@

```{r chart1b}
chart1 <- read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%")) %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)),
                     limits = c(0, 50)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Age 70 Percentage of People Who Fail to Replace 80% of Age 50-59 Earnings"),
      chart1,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2, 30, 1, 1))
```

@@

```{r chart1c}
chart1 <- read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%", "80-85%")) %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)),
                     limits = c(0, 50)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Age 70 Percentage of People Who Fail to Replace 85% of Age 50-59 Earnings"),
      chart1,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(2, 30, 1, 1))
```

@@

```{r chart1d}
chart1 <- read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%", "80-85%", "85-90%")) %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)),
                     limits = c(0, 50)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Age 70 Percentage of People Who Fail to Replace 90% of Age 50-59 Earnings"),
      chart1,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 30, 1, 1))
```

### 100% replacement rate

```{r chart1e}
chart1 <- read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%", "75-80%", "80-85%", "85-90%", "90-95%", "95-100%")) %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)),
                     limits = c(0, 50)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Age 70 Percentage of People Who Fail to Replace 100% of Age 50-59 Earnings"),
      chart1,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 30, 1, 1))
```

## Chart 2: Retirement Incomes are Increasing

```{r chart2}
chart2 <- read_csv("data/figure2.csv") %>%
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, ncharts_aftertax_income_P50)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::dollar(ncharts_aftertax_income_P50, largest_with_cents = 0)), 
            vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Retirement Incomes are Increasing"),
      subtitler("Median age-70, per-capita, price-adjusted shared annuitized income less taxes"),
      chart2,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 1, 30, 1, 1))
```

## Chart 3: The Gender Gap in Social Secuirty Benefits is Narrowing

```{r, chart3}
chart3b <- read_csv("data/figure3b.csv") %>%
  mutate(male = recode(male, 
                       `1.Male` = "Male",
                       `2.Female` = "Female")) %>%  
  filter(doby %in% cohorts) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, Ownssb_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(Ownssb_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 0.75), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("The Gender Gap in Social Security Benefits is Narrowing"),
      subtitler("Median Age-70 Price-Adjusted Social Security Benefits by Sex"),
      chart3b,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 2, 30, 1, 1))
```

@@

```{r chart4}
chart4 <- read_csv("data/figure4.csv") %>%
  mutate(male = recode(male, 
                       `1.Male` = "Male",
                       `2.Female` = "Female")) %>%
  filter(doby %in% cohorts) %>%
  filter(!is.na(male)) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, lifetime_earn_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(lifetime_earn_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 1), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Growth in Earnings, Especially by Women, Will Boost Future Retirement Incomes"),
      subtitler("Median price-adjusted earnings from ages 25 to 69 at age 70 by sex"),
      chart4,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 2, 30, 1, 1))
```

@@

```{r chart5}
benefits <- c("Worker only", "Worker supplemented by\nspousal or survivor", "Spouse or survivor only")

chart5 <- read_csv("data/figure5.csv") %>%
  filter(doby %in% cohorts) %>%
  select(doby,
         `Worker supplemented by spousal or survivor` = dualben_Mean,
         `Worker only` = wrkonly_Mean,
         `Spouse or survivor only` = auxonly_Mean) %>%
  gather(key = "benefit_type", value = "share", -doby) %>%
  mutate(benefit_type = recode(benefit_type, 
                               `Worker supplemented by spousal or survivor` = "Worker supplemented by\nspousal or survivor")) %>%  
  mutate(benefit_type = factor(benefit_type, levels = benefits)) %>%
  mutate(doby = rename_cohort(doby)) %>%
  ggplot(aes(doby, share, fill = benefit_type)) +
  geom_col(position = "dodge") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), labels = scales::percent_format(accuracy = 1)) +
  labs(x = NULL,
       y = NULL) +
  remove_ticks()

# create the output plot
plotr(titler("Women’s Social Security Benefit Types are Changing"),
      subtitler("Social Security benefit type at age 70 for female beneficiaries (%)"),
      chart5,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 2, 30, 1, 1))
```

## Chart 6: Racial and ethnic disparities in retirement income will persist

```{r chart6}
chart6 <- read_csv("data/figure6.csv") %>%
  filter(doby %in% cohorts) %>%
  filter(!is.na(raceeth)) %>%
  filter(raceeth != "4.Other") %>%
  mutate(raceeth = recode(raceeth, 
                          `1.White, Non-Hisp` = "White, non-Hispanic",
                          `2.Black, Non-Hisp` = "Black, non-Hispanic",
                          `3.Hispanic` = "Hispanic"
                          )) %>%  
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, ncharts_aftertax_income_P50, fill = raceeth)) +
  geom_col(position = "dodge") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15)), 
                     labels = scales::dollar) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks()

# create the output plot
plotr(titler("Racial and Ethnic Disparities in Retirement Income Will Persist"),
      subtitler("Age-70, per-capita, price-adjusted, shared annuitized income less taxes by race and ethnicity"),
      chart6,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 1, 30, 1, 1))
```

## Chart 7: Social Security Is a Pillar of Retirement Security {.tabset}

* Quintiles are based on per-capita, price-adjusted, shared annuitized income with federal taxes, state taxes, payroll taxes and the Medicare surtax at age 70.
* Values are the mean of the different sources of income in each quintile.

Financial income = per-capita interest + per-capita dividends + per-capita rental income + per-capita IRA withdrawals

Other income = pcNotModel_Mean

### Arrangement 1

```{r chart7}
incomes <- c("Other income", "Financial income", "DB pension income", "Earnings", "Social Security")

read_csv("data/figure7.csv") %>%
  filter(doby %in% cohorts) %>%
  mutate(`Financial income` = PCwlthinc_Mean + PCRetinc_Mean, 
         `Other income` = pcNotModel_Mean) %>%
  select(nchartQuin,
         doby,
         Earnings = PCearn_Mean, 
         `Social Security` = PCssb_Mean, 
         `DB pension income` = PCdbinc_Mean, 
         `Financial income`, `Other income`) %>%
  gather(key = "income_type", value = "income", Earnings, `Social Security`, `DB pension income`, `Financial income`, `Other income`) %>%
  mutate(doby = rename_cohort(doby, two_lines = FALSE)) %>% 
  mutate(income_type = factor(income_type, levels = incomes)) %>%
  ggplot(aes(as.character(nchartQuin), income, fill = income_type)) +
  geom_col(position = "fill") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     labels = scales::percent) +
  facet_wrap(~doby) +
  labs(title = "Major Sources of Income at Age 70 by Income Quintile",
       x = "Income quintile",
       y = NULL) +
  remove_ticks()  
```

### Arrangement 2

```{r chart7-alt}
incomes <- c("Other income", "Financial income", "DB pension income", "Earnings", "Social Security")

chart7 <- read_csv("data/figure7.csv") %>%
  filter(doby %in% cohorts) %>%
  mutate(`Financial income` = PCwlthinc_Mean + PCRetinc_Mean, 
         `Other income` = pcNotModel_Mean) %>%
  select(nchartQuin,
         doby,
         Earnings = PCearn_Mean, 
         `Social Security` = PCssb_Mean, 
         `DB pension income` = PCdbinc_Mean, 
         `Financial income`, `Other income`) %>%
  gather(key = "income_type", value = "income", Earnings, `Social Security`, `DB pension income`, `Financial income`, `Other income`) %>%
  mutate(income_type = factor(income_type, levels = incomes)) %>%
  ggplot(aes(doby, income, fill = income_type)) +
  geom_col(position = "fill") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), 
                     labels = scales::percent) +
  facet_wrap(~as.character(nchartQuin)) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# create the output plot
plotr(titler("Social Security Is a Pillar of Retirement Security"),
      subtitler("Major sources of income at age 70 by income quintile"),
      chart7,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 1, 30, 1, 1))
```

@@

```{r, chart9}

scheduled <- read_csv("data/figure1.csv") %>%
  mutate(law = "Scheduled law")

payable <- read_csv("data/figure9.csv") %>%
  mutate(law = "Payable law") %>%
  rename(ncharts_reprate = ncharts_reprate_payable)

chart9 <- bind_rows(scheduled, payable) %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%")) %>%
  filter(doby %in% cohorts) %>%
  group_by(doby, law) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ungroup() %>%
  mutate(law = factor(law, levels = c("Scheduled law", "Payable law"))) %>%
  mutate(doby = rename_cohort(doby)) %>%  
  ggplot(aes(doby, rep_rate_threshold, fill = law)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), 
            vjust = -1,
            position = position_dodge(width = 0.8)) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(x = "Birth Cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

# create the output plot
plotr(titler("Social Security Insolvency Will Damage Retirement Security"),
      subtitler("Age 70 Percentage of People Who fail to Replace 75% of Age 50-59 Earnings"),
      chart9,
      caption,
      sourcer("DYNASIM4, ID963"),
      heights = c(1.8, 1, 30, 1, 1))
```

## Chart 12
